Nonparametric Block Bootstrap Kolmogorov-Smirnov Goodness-of-Fit Test

### 2024-05-14 manuscript/manuscript.tex
cited my paper

Developing a fully nonparametric solution for the KS 
tests in the presence of serially dependent data presents a significant 
challenge. The null distribution's characteristics are intricately linked to 
the structure of the serial dependence, which can vary widely in practical 
situations. Employing a nonparametric method would necessitate defining a 
specific model for this dependence, despite the primary focus being on 
evaluating the marginal distribution of a stationary series. To date, a bias 
correction method for block bootstrap, akin to the NPB
approach of \citet{babu2004goodness} for independent data,
has not been established. This study seeks 
to bridge this gap by introducing a bias correction technique for the 
nonparametric block bootstrap (NPBB), tailored for use in scenarios where the 
hypothesized distribution has unspecified parameters and the data 
exhibit serial dependence. Our approach reduces to that of
\citet{babu2004goodness} when the data are independent.

@@

Consider a stationary time series $\{X_t: t = 1, \ldots, n\}$ with length~$n$.
We are interested in testing whether or not $X_t$ follows a distribution in a
parametric family of distribution~$F$ indexed by a parameter
vector~$\theta$. That is, the null hypothesis is
\[
  H_0: X_t \sim F(\cdot \mid \theta), \quad t = 1, \ldots, n,
\]
for some unspecified parameter $\theta$.
The alternative hypothesis $H_A$ is that the marginal distribution of $X_t$ does
not follow~$F$ for any parameter value~$\theta$. This is a challenging situation
because both the parameters and the serial dependence structure are unknown.

@@

\eds{Please check consistency with how you refer to $F$.  In 
Equation~\eqref{eq:ks_standard}, it is $F(x; \theta_0)$ where the data and 
parameter arguments are separated by a semicolon.  At the beginning of 
Section~\ref{sec:methods}, it is $F(\cdot \mid \theta)$, with the vertical bar
separating the data argument from the parameter argument (and no 0 subscript
either).   Then in this first 
subsection it is $F(x; \hat\theta_n)$ with a semicolon separating the two 
arguments.  Then immediately above its use is mixed with $F(x)$ without a 
parameter argument (implying it is the true parameter $\theta$). This continues
throughout the document. I suggest either using consistent notation throughout, 
or explicitly defining any shortened/simplified notation at its first use.}
\mc{I believe the vertical bar is to indicate that the parameters are 
unspecified}

@@

These distributions
were chosen to compare results on normal and non-normal
error structures. The specific parameters were chosen because the distributions 
are very similar and their
first two moments are the same. 
For the purposes of 
evaluating if the test holds it size, when $X_t \sim N(8, 8)$, we tested that the 
marginal distribution is from the
Normal family, or 
$X_t \sim N(\cdot \mid \mu, \sigma^2), \quad t = 1, \ldots, n$
for some unspecified $\mu$ and $\sigma$. When $X_t \sim \Gamma(8, 1)$, we tested
that the marginal distribution family is from the Gamma family,
or
$X_t \sim \Gamma(\cdot \mid \alpha, \beta), \quad t = 1, \ldots, n$.
for some unspecified $\alpha$ and $\beta$.
\eds{Vertical bar vs semicolon to separate data and parameter arguments.}
\mc{I believe the vertical bar is indicate that the parameter arguments are 
unspecified}
For the block
bootstrap step,
we used $B = 1000$ and $l = \lceil n^{1/3} \rceil$.
For each setting for $F$, $\tau$, and $n$, we replicate the method 1000 times 
to get the distribution of the p-values $p_r$ for
$r \in \{1, \dots, 1000\}$
for the test when applied to samples from the same data generating process.
\eds{I assume $r$ is for replicate?  Please define and include how many 
total replicates you are using.} \mc{addressed}

@@

\eds{can Mathew's AJUR paper be cited somewhere in this document?}

>>>>

Developing a fully nonparametric solution for the KS 
tests in the presence of serially dependent data presents a significant 
challenge. The null distribution's characteristics are intricately linked to 
the structure of the serial dependence, which can vary widely in practical 
situations. Employing a nonparametric method would necessitate defining a 
specific model for this dependence, despite the primary focus being on 
evaluating the marginal distribution of a stationary series. To date, a bias 
correction method for block bootstrap, akin to the NPB
approach of \citet{babu2004goodness} for independent data,
has not been established. This study seeks 
to bridge this gap by introducing a bias correction technique for the 
nonparametric block bootstrap (NPBB), tailored for use in scenarios where the 
hypothesized distribution has unspecified parameters and the data 
exhibit serial dependence. Our approach reduces to that of
\citet{babu2004goodness} when the data are independent. 
As noted by 
\citet{chandy2024sample}, a sample greater than 1600 may be necessary for 
block bootstrap confidence intervals to have the right coverage 
rates of parameters. 
Therefore, although this study uses block bootstrap in a different setting,
we expect that a large sample size may be required when the data is serially
dependent.

@@

Consider a stationary time series $\{X_t: t = 1, \ldots, n\}$ with length~$n$.
We are interested in testing whether or not $X_t$ follows a distribution in a
parametric family of distribution~$F$ indexed by a parameter
vector~$\theta$. That is, the null hypothesis is
\[
  H_0: X_t \sim F(\cdot ; \theta), \quad t = 1, \ldots, n,
\]
for some unspecified parameter $\theta$.
The alternative hypothesis $H_A$ is that the marginal distribution of $X_t$ does
not follow~$F$ for any parameter value~$\theta$. This is a challenging situation
because both the parameters and the serial dependence structure are unknown.

@@

\eds{Please check consistency with how you refer to $F$.  In 
Equation~\eqref{eq:ks_standard}, it is $F(x; \theta_0)$ where the data and 
parameter arguments are separated by a semicolon.  At the beginning of 
Section~\ref{sec:methods}, it is $F(\cdot \mid \theta)$, with the vertical bar
separating the data argument from the parameter argument (and no 0 subscript
either).   Then in this first 
subsection it is $F(x; \hat\theta_n)$ with a semicolon separating the two 
arguments.  Then immediately above its use is mixed with $F(x)$ without a 
parameter argument (implying it is the true parameter $\theta$). This continues
throughout the document. I suggest either using consistent notation throughout, 
or explicitly defining any shortened/simplified notation at its first use.}
\mc{switched everything to semicolons}

@@

These distributions
were chosen to compare results on normal and non-normal
error structures. The specific parameters were chosen because the distributions 
are very similar and their
first two moments are the same. 
For the purposes of 
evaluating if the test holds it size, when $X_t \sim N(8, 8)$, we tested that the 
marginal distribution is from the
Normal family, or 
$X_t \sim N(\cdot ; \mu, \sigma^2), \quad t = 1, \ldots, n$
for some unspecified $\mu$ and $\sigma$. When $X_t \sim \Gamma(8, 1)$, we tested
that the marginal distribution family is from the Gamma family,
or
$X_t \sim \Gamma(\cdot ; \alpha, \beta), \quad t = 1, \ldots, n$.
for some unspecified $\alpha$ and $\beta$.
\eds{Vertical bar vs semicolon to separate data and parameter arguments.}
\mc{changed everything to semicolon}
For the block
bootstrap step,
we used $B = 1000$ and $l = \lceil n^{1/3} \rceil$.
For each setting for $F$, $\tau$, and $n$, we replicate the method 1000 times 
to get the distribution of the p-values $p_r$ for
$r \in \{1, \dots, 1000\}$
for the test when applied to samples from the same data generating process.
\eds{I assume $r$ is for replicate?  Please define and include how many 
total replicates you are using.} \mc{addressed}

@@

\eds{can Mathew's AJUR paper be cited somewhere in this document?}
\mc{addressed}
